\begin{bf}THE INFORMATION CONTAINED IN THIS DOCUMENT IS PROVIDED ON AN “AS-IS” BASIS, WITHOUT WARRANTY OF ANY KIND, EITHER
EXPRESS OR IMPLIED, INCLUDING THE IMPLIED WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE, OR
NON-INFRINGEMENT. SOME JURISDICTIONS DO NOT ALLOW THE EXCLUSION OF IMPLIED WARRANTIES, SO THE ABOVE EXCLUSION
MAY NOT APPLY TO YOU. IN NO EVENT WILL TERADATA CORPORATION BE LIABLE FOR ANY INDIRECT, DIRECT, SPECIAL, INCIDENTAL,
OR CONSEQUENTIAL DAMAGES, INCLUDING LOST PROFITS OR LOST SAVINGS, EVEN IF EXPRESSLY ADVISED OF THE POSSIBILITY OF
SUCH DAMAGES.\\
\end{bf}


\begin{small}
The information contained in this document may contain references or cross-references to features, functions, products, or services that are
not announced or available in your country. Such references do not imply that Teradata Corporation intends to announce such features,
functions, products, or services in your country. Please consult your local Teradata Corporation representative for those features, functions,
products, or services available in your country.\\
Information contained in this document may contain technical inaccuracies or typographical errors. Information may be changed or updated
without notice. Teradata Corporation may also make improvements or changes in the products or services described in this information at any
time without notice.\\
To maintain the quality of our products and services, we would like your comments on the accuracy, clarity, organization, and value of this
document. Please e-mail: teradata-books@lists.teradata.com\\
Any comments or materials (collectively referred to as “Feedback”) sent to Teradata Corporation will be deemed non\-confidential. Teradata
Corporation will have no obligation of any kind with respect to Feedback and will be free to use, reproduce, disclose, exhibit, display, transform,
create derivative works of, and distribute the Feedback and derivative works thereof without limitation on a royalty-free basis. Further, Teradata
Corporation will be free to use any ideas, concepts, know-how, or techniques contained in such Feedback for any purpose whatsoever, including
developing, manufacturing, or marketing products or services incorporating Feedback.\\
\bf{Copyright © 2005 - 2013 by Teradata Corporation. All Rights Reserved.}
\end{small}
